Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-06 Paper/paper.tex
added power law figures

% 
\begin{figure}
\centering    
\includegraphics[width=1.\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N49_Log.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
% 
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
% 
}
\label{fig:TT_Lambda_vs_Lambda_L500_2000_CI90_0_AllInOne}
\end{figure}
%
% 
\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}
% 
% 
First we show a crude calculation which tells us that approximately $8$ (or $16$) 
observations
of NSBH signals with $\rho\geq 10$ distributed uniformly in effective volume, would
give us similarly accurate a measurement of $\lambdans$ as would a single detection
with $\rho=50$ (or $\rho=70$).

>>>>

% 
\begin{figure}
\centering    
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsN_vs_Lambda.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
% 
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
% 
}
\label{fig:TT_PowerLawLambdaErrorVsN}
\end{figure}
%

% 
\begin{figure*}
\centering    
\includegraphics[width=\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N79_Log.pdf}
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsLambda_vs_N.pdf}
\caption{This figure shows the relative uncertainty in the measurement of $\lambdans$,
as a function of $\lambdans$ itself. The drawn curves are cumulative, in the sense 
that the $N=n$ curve includes information from all of the first $n$ observed events.
Those corresponding to the first $N\leq 5$ events are shown in fading shades of red,
with the ones for higher value of $N$ being shown in grey (going from light to dark in
proportion to $N$).
Green dash-dotted lines are contours of $y=x^{-(1+1/5)}$.
% 
\prayush{We note that the measurement uncertainty from a population follows the
equation for the green lines.}
% 
}
\label{fig:TT_Lambda_vs_Lambda_L500_2000_CI90_0_AllInOne}
\end{figure*}
%
% 
\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}
% 
% 
First we show a crude calculation which tells us that approximately $8$ (or $16$) 
observations
of NSBH signals with $\rho\geq 10$ distributed uniformly in effective volume, would
give us similarly accurate a measurement of $\lambdans$ as would a single detection
with $\rho=50$ (or $\rho=70$).
